\section{Introduction}
Learning a new language from language learning websites is 
time consuming. It is, therefore, necessary to make second 
language learning attractive and efficient. Further, since habitual 
learning is effective, we seek to interleave language leaning with 
a popular daily activity. Reading news online is once such 
activity. 
% Muthu: can you find a citation that says lot of people read new online?.
Further recent increase in the popularity of 
portable devices has made online news reading popular than ever 
before~\cite{yarlh2012}. We leverage on this culture to provide 
users of news websites with an opportunity to learn a second 
language.

We propose a system to enable online news readers to efficiently learn 
a new language while they are reading news on news websites. We propose 
a Chrome extension which would run on the client (Chrome web browser) 
when readers visit news websites on a preconfigured list.

% Muthu: can you ealborate a liitle bit? That is, find a citaion that says
% grammar learning, etc., is less important or useful than learning vocabulary (words)
% in a new second langauge 
Learning a new vocabulary is the most time consuming and boring part of 
language learning~\footnote{\url{https://neltachoutari.wordpress.com/tag/vocabulary/}}. 
Perhaps, this justifies the poor adoption of current second language learning 
systems. We, therefore, focus on enabling language learners build their vocabulary 
efficiently while providing them with an enjoyable user experience.

There are many existing language learning software, which, fall into two categories, 
learning by lessons and learning vocabularies. In the first category, 
%learning in lessons, they manually design some lessons to help their 
lessons are purposefully designed to help users easily learn a foreign language.
Duolingo\footnote{\url{https://www.duolingo.com/}} is a popular websites in this category. 
For the second categoryusers are guided to recite lists of words, or provided with 
a translation for their input word in the foreign language. 
Google Translate \footnote{\url{https://translate.google.com/}} stands out in this 
category. The service is available as desktop / mobile / web software including a 
chrome extension. We mainly compare our system  with the aforementioned two software.
Table~\ref{table:difference_summary} summarises important differences between 
our system and all these existing tools. Each difference serves as a motivation 
for developing our extension.

``Duolingo is a free language-learning and crowdsourced text translation 
platform''\footnote{\url{http://en.wikipedia.org/wiki/Duolingo}}.
Most people start to use Duolingo when they know a little or nothing about 
the new language. They starting from some basic lessons and improve step by step.
However, our target audience 
is a mix novice and intermediate level learners of the foreign language. 
We can not only help beginners learn 
a new language but also help them continue their learning by allowing them to practice 
their foreign language. There are also a lot articles with their translations in 
Duolingo, but all the articles and their translations are manually added by 
Duolingo or users from Duolingo. Therefore, parallel articles in Duolingo are old and 
limited. However, our chrome extension is always working even for those up to the 
minute news and our user can just practice their foreign language in their daily 
readings.

\textbf{Google Translate:} ``Highlight or right-click on a section of text and click
on Translate icon next to it to translate it to your 
language''\footnote{\url{http://en.wikipedia.org/wiki/Google_Chrome_Extensions}}. 
% Tao: please cite
Google Translate is a chrome extension that displays only the translation when user 
select a section, which can be a word, a phrase, a sentence or even a whole page. 
Our chrome extension will translate a single word only, and display the translation,
following with the pronunciations and example sentences to help user understand and 
remember this word. Compared with our extension, Google Translate is more like an extension 
to help user understand the content of the page. Furthermore, our extension will display 
the most appropriate translation as it will refer to the context of the word.

%\begin{table}[ht]
%  \caption{Summary of the differences}
%  \label{table:difference_summary}
%  \begin{center}
%  \begin{tabular}{| p{2.4cm} | p{1.2cm} | p{1.2cm} |  p{1.2cm} |}
%    \hline
%    & Duolingo & Google Translate & Chrome Extension \\
%    \hline
%    Lessons & Yes & No & No \\
%    \hline
%    User's foreign language level & Low & Low-High & Low-High \\
%    \hline
%    Time consuming & Yes & No & No\\
%    \hline
%    Resource & Limited & Infinite & Infinite \\
%    \hline
%    Customizable & Yes & No & Yes \\
%    \hline
%    Link to External Dictionary & No & No & Yes \\
%    \hline
%  \end{tabular}
%  \end{center}
%\end{table}