\section{Platform Viability and Usability Survey}

We have thus far described and evaluated two critical components that
can benefit from capturing the learner's news article context.  In the
larger context, we also need to check the viability of second language
learning intertwined with news reading.  In a requirements survey
prior to the prototype development, two-thirds of the respondents
indicated that although they have used language learning software,
they use it infrequently (less than once per week), giving us motivation for our development.  

Post-prototype, we conducted a summative survey to assess whether our
prototype product satisfied the target niche, in terms of interest,
usability and possible interference with normal reading activities.
We gathered 16 respondents, 15 of which were between the ages of
18--24.  11 (the majority) also claimed native Chinese language
proficiency.  

% Min: Yue, need your input here.  Something like the below.
The respondents felt that the extension platform was a viable language
learning platform (3.4 of 5; on a scale of 1 ``disagreement'' to 
5 ``agreement'') and that they would like to try it when available
for their language pair (3 of 5).

In our original prototype, we replaced the original English word with
the Chinese translation.  While most felt that replacing the original
English with the Chinese translation would not hamper their reading,
they still felt a bit uncomfortable (3.7 of 5).  This finding
prompted us to review and change the default setting of the learning
tooltip to simply add an underline to hint at the tooltip presence.